Phenotype selection

### 2022-02-24 analysis/phenotype_selection.Rmd
udpate phenotpye selection

Using the sex-specific summary statistics, heterogeneity between sexes was calculated. IVs that showed significant evidence of heterogeneity between sexes were included (p < 0.05/[number of IVs]). After filtering IVs with significant heterogeneity, phenotypes were filtered to again have IVs < `r num_IVs_threshold`.

@@

Lastly, left-side body traits (highly correlated with right-side) were removed and all 'qualifications' data (corresponding to field [6138](https://biobank.ctsu.ox.ac.uk/showcase/field.cgi?id=6138)) because data is roughly captured with continuous variables (such as years of education).

>>>>

Using the sex-specific summary statistics, heterogeneity between sexes was calculated. IVs that showed significant evidence of heterogeneity between sexes were excluded (p < 0.05/[number of IVs]). After filtering IVs with significant heterogeneity, phenotypes were filtered to again have IVs < `r num_IVs_threshold`.

@@

Lastly, we removed several duplicated and redundant phenotypes. Specifically, all left-side body traits (highly correlated with right-side) were removed and we also retained only one of the duplicated phenotypes for BMI and weight (retaining data fields 21001 and 21002, respectively). Additionally, all “qualifications” data was removed (corresponding to field 6138) due to the availability of finer-scale correlated variables, such as “age completed full time education” (data field 845).
